\documentclass[10pt,a4paper]{report}
\input{preamble.tex}
\input{tikzpreamble.tex}
\input{tikzpreamble pneumatics.tex}
\input{acronyms.tex}
\input{requirements.tex}
\input{researchquestions.tex}
% \input{workpackages.tex}

% Define the Title Page
\title{\textbf{Project SHARP- Power Generation and Delivery System} \\ \vspace{1cm}
\textbf{Technical Report}}
\author{Emil Boot}
\date{\today}

\begin{document}
% Import sections from the sections folder
\input{sections/titlepage.tex}
\input{sections/change_record.tex}

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
TBD

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
This thesis seeks the answer to the research question: `To what extent is a hydrogen fuel cell based power generation and feed system that integrates a Solid Flow's cool gas generator and Stellar Space Industries' flow control unit feasible for extending the mission time for UAV's'

This document covers the design process of this power generation and feed system. The system will use hydrogen from a Cool Gas Generator (CGG) that stores hydrogen as solid \ce{NaBH4} and produces a constant stream of hydrogen gas. This hydrogen gas is then fed to a Fuel Cell to generate power. A battery is used as a power buffer to support varying loads while consuming a constant amount of hydrogen. The Fuel Cell periodically cleans excess water from its fuel intake by performing purge events during which it uses hydrogen at an increased rate. To make this compatible with the constant flow of the CGG a buffer volume is used to store a small amount of hydrogen for this purpose. A Flow Control Unit (FCU) is used to provide hydrogen from this buffer to the Fuel Cell at the correct pressure.

To verify the design, a test bench has been developed that includes a Fuel Cell, CGG flow equivalent, FCU, battery and motor and propeller as representative load, as well as numerous sensors to document the system behaviour. Preliminary results of this test bench are presented in this thesis which suggest that the designed power generation and feed system is capable of more than doubling the mission time of a UAV. However, due to neither a CGG or a hydrogen tank being available during the project, final tests using this test bench are still waiting to be performed.

% Table of Contents:
\newpage
{\large \tableofcontents}
\newpage
\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

\input{sections/introduction.tex}
\input{sections/research.tex}
\input{sections/requirements.tex}
\input{sections/concept_design.tex}
\input{sections/detailed_design.tex}
\input{sections/results.tex}
\input{sections/conclusion.tex}
\input{sections/recommendations.tex}

\begin{appendices}
    \input{project plan sections/appendix_a.tex}
\end{appendices}

\newpage
\bibliography{references}
\end{document}
