\section{Background}

% \textit{
%     This chapter should contain a description of the company,
%     who they are and why do they want to do the project.
%     Other stakeholders should also be mentioned and what interest they have in the project.
%     A brief overview of the report structure can also be given here.
% }

% \begin{itemize}
%     \item Talk about SSI, the development of (atmosphere breathing) propulsion systems for small satellites.
%     \item Development state of the valve and why testing it in a relevant environment is important.
%     \item Solid Flow and their CGG's which together with the valve can be a weight efficient fuel delivery system.
%     \item This would make for a nice aviation energy transition project, hence the drone.
%     \item Internship is only a part of SHARP, focusing on developing the H2 power system.
%     \item This report is made in accordance with the guidelines in the book '\emph{Project Management}'~\cite{Grit2011}.
% \end{itemize}

% \textit{
%     This leads to testing the valve being the main goal.
%     An alternative is talking about how batteries are too heavy for electric flight and have aviation energy transition as main goal.
%     \newline
%     % \\Do I also include reference projects such as the NLR drone, or is that in literature report later?
%     \\Problem statement:
%     \\Batteries are too heavy for electric flight, OR,
%     \\Need an affordable way to test the valve in a relevant environment
% }

\subsection*{Stellar Space Industries}
\gls{ssi} is a Dutch aerospace company located in Noordwijk near \gls{esa}'s ESTEC facility.
\gls{ssi} specialises in high precision manufacturing capabilities
and covers the entire product development cycle including design, machining, assembly, integration and testing.
Their production facility is equipped with high-precision machining and testing equipment.

In collaboration with \gls{esa}, \gls{ssi} is developing a novel electrodeless electric propulsion system for small satellites.
This propulsion system aims to increase efficiency, lifespan and reliability compared to current state-of-the-art electric propulsion systems.
\gls{ssi} is currently in their second phase of development where they aim to design build and test the entire system in-house.

Presently, several subsystems of the propulsion system are being developed and tested concurrently.
During the development of these subsystems, \gls{ssi} is also looking for opportunities to apply the technology of each component in other applications.
One of the subsystems that is currently ready for testing and application is \gls{ssi}'s \gls{fcu} which is a high-precision valve that can control the mass flow of gaseous propellants.


\subsection*{Project SHARP}
In order to find a relevant application for their \gls{fcu}, \gls{ssi} has initiated the \gls{sharp} project.
\gls{sharp} is a joint investigation between \gls{ssi} and \glsxtrlong{sf}, a Dutch company specialising in the development of solid hydrogen storage systems.
The goal of \gls{sharp} is to investigate the feasibility of hydrogen-fuelled drones that utilise solid-state hydrogen storage.
In this collaboration, \glsxtrlong{sf} provides the cool gas generator (CGG), a system capable of producing gaseous hydrogen on demand from solid hydrogen storage.
\gls{ssi} contributes its expertise in flow control systems for electric propulsion, which may be adapted for hydrogen-based applications.

\gls{sharp} is conducted under the \gls{lit} program of the RVO of the Dutch government, which aims to advance sustainable aviation technologies. \gls{sharp} aims to contribute to the aviation energy transition by providing a scalable, weight and volume efficient energy source that is CO\textsubscript{2} and NO\textsubscript{x} neutral. \gls{sharp} first aims to demonstrate the feasibility of the technology in drone applications, allowing future projects to scale the technology to larger aircraft and replace traditional jet fuel-based propulsion systems.

\subsection*{SHARP --- Power Generation and Delivery System}
This document considers the project plan for a subsystem of the \gls{sharp} project, specifically the development of the power generation and delivery system. This part of the \gls{sharp} project is conducted as a graduation internship. Throughout this document the part of \gls{sharp} that falls under the graduation internship will be referenced as \gls{sharpps}.

\newpage
