\section{Scope}
% Exactly what is included and excluded from the project scope

% Describe activities on the border and wether they are included or excluded
% Begin and end dates
% Maximum budget
% Required resources (randvoorwaarden)

% From original project assignment:
% Designing a system overview of the complete power generation and feed system.
% Selecting components for the hydrogen fuel cell, intermediate electrical storage, and drone interfaces.
% Developing the electrical design of the power generation and feed system (fuel cells, intermediate storage, and connection to the COTS drone).
% Implementing mechanical modifications to the COTS drone to ensure system compatibility.
% Performing assembly and integration of the power generation and feed system into the drone.
% Conducting ground testing of the power generation and feed system using a gaseous hydrogen source.
% Compiling a comprehensive report of all findings and results.

% Is defining the mission scenario part of the project scope?
% Maybe adapt COTS drone to test bench or even custom drone. Would be nice if we can specify that already.

% \textit{
%     Describe activities on the border and whether they are included or excluded.
%     \\Begin and end dates.
%     \\Maximum budget.
%     \\Required resources (randvoorwaarden)
% }

As SHARP-PS is conducted as an internship, the start and end dates are fixed. The internship runs from 2 February 2026 to 14 June 2026, and as such SHARP-PS will follow those dates strictly. At this time, the exact time requirement for the SHARP-PS project activities can not yet be accurately determined, only estimated. Therefore, the scope of the project is made slightly flexible to satisfy the exact time requirement of the internship.

This chapter defines a minimum scope which concerns the development and testing of a power generation and feed system for a commercial off-the-shelf (COTS) or custom built UAV. The power generation and feed system will first be tested independent of the UAV. This independent setup will be referred to as the test bench setup. The minimum scope includes the selection or design of the UAV and design, manufacturing and testing of the test bench setup. If time allows, manufacturing and testing of the power system integrated in the UAV may be included into the scope of SHARP-PS as well.

% This chapter defines a minimum scope which concerns the development and testing of an independent power generation and feed system that is ready to be integrated in a UAV, this setup is also referred to as a test bench setup. If time allows, integrating this power system into a commercial off-the-shelf (COTS) or custom built UAV may be included in the scope of SHARP-PS as well.

The following lists describe the scope of the SHARP-PS project and exactly which activities are part of it. This is done by listing certain activities that fall particularly at the border of the project, and clarifying whether or not they are part of SHARP-PS, the SHARP-PS extended scope, SHARP as a whole or not part of SHARP at all.

Activities that \textbf{are} included in SHARP-PS:
\begin{itemize}
    \item Selecting a suitable COTS or custom built UAV.
    \item Designing a system overview of the complete power generation and feed system.
    \item Selecting components for the hydrogen fuel cell and intermediate energy storage
    \item Developing the electrical design of the power generation and feed system.
    \item Performing assembly and integration of the power generation and feed system.
    \item Conducting ground testing of the power generation and feed system using a gaseous hydrogen source.
    \item Compiling a comprehensive report of all findings and results.
\end{itemize}

Activities that initially \textbf{are not} included in SHARP-PS, but \textbf{may} be included in SHARP-PS if allowed by time:
\begin{itemize}
    \item Selecting components for the UAV interfaces.
    \item Implementing mechanical modifications to the UAV to ensure system compatibility.
    \item Integrating the power system developed as part of the test bench setup with the selected UAV.
    \item Conducting flight testing of the integrated power system and UAV using a CGG hydrogen source.
\end{itemize}

Activities that have already been completed by SSI (\textbf{not} part of SHARP-PS):
\begin{itemize}
    \item Developing the flow control unit.
    \item Testing the FCU in lab conditions.
    \item Adapting the FCU for hydrogen purposes.
\end{itemize}

Activities that \textbf{are not} included in SHARP-PS but are part of the larger SHARP project:
\begin{itemize}
    \item Developing a (closed loop) driver for the flow control unit.
    \item Designing a mission scenario for solid hydrogen based UAV's.
    \item Setting requirements for the hydrogen CGG.
    \item Developing and producing the hydrogen CGG.
\end{itemize}


\newpage
% Activities that \emph{are} included (from original project assignment):
% \begin{itemize}
%     \item Designing a system overview of the complete power generation and feed system.
%     \item Selecting components for the hydrogen fuel cell, intermediate electrical storage, and drone interfaces.
%     \item Developing the electrical design of the power generation and feed system.

%           % \item Implementing mechanical modifications to the COTS drone to ensure system compatibility.

%     \item Performing assembly and integration of the power generation and feed system into the drone.
%     \item Conducting ground testing of the power generation and feed system using a gaseous hydrogen source.
%     \item Compiling a comprehensive report of all findings and results.
% \end{itemize}

% \textit{
%     Is defining the mission scenario part of the project scope?
%     \\Maybe adapt COTS drone to test bench or even custom drone. Would be nice if we can specify that already.
%     \\Add some activities that are explicitly excluded from the project scope?
% }

% \newpage
