\section{Project Organisation}

% \textit{
%     This chapter should contain a description of the project organisation.
%     Who are the team members and what are their roles and responsibilities.
%     Contact details of team members and other stakeholders can also be given here.
%     The meeting frequency and dates can also be mentioned as well as the digital workspace that will be used.
% }

% \begin{itemize}
%     \item email, phone of me and Imre (and others?)
%     \item Contact details of Solidflow? (outside of scope maybe)
%     \item Weekly progress meetings on Thursdays
%     \item The onedrive space for files
%     \item Decide on a place for CAD files?
% \end{itemize}

This chapter will describe the organisational structure that the SHARP-PS project will be conducted in. The SHARP-PS project is an internship project and as such will be carried out as an individual project by a single intern. Both the university and the company provide a supervisor that can provide support to the intern. The communication details of the intern and supervisors is listed in table~\ref{table:comms}.

\subsection*{Supervisor communication}
There will be weekly progress meetings with the intern and the company supervisor on Thursdays at 14.00. This meeting will serve to keep the company supervisor up-to-date with the progress of the project and allow them to address concerns regarding planning or quality. In addition to this, the progress meetings serve as an opportunity for the intern to ask questions and request support from the company supervisor if necessary.

Communication between the intern and the university supervisor will happen through email.

\subsection*{Document location}
Files regarding the SHARP-PS document will be stored in the OneDrive environment for project SHARP. This environment has been shared with the intern already. The location within this environment that is dedicated to the SHARP-PS project is the following:
\\\textit{`LIT-R\&D-SHARP-SF-SSI --- Phase A Documentation/WP3\_Hydrogen\_Transport\_System'}

Any documents that are required by the University, but are not required by the company wil be saved in the OneDrive environment for external collaboration:
\\\textit{`SSI External Collaboration --- InHolland\_Graduation\_Internship\_Emil/Documents'}
\\These documents will be handed in at the university through the OnStage environment. The OnStage environment is also the leading place for listing the documents that need to be handed in and their respective deadlines.

\begin{table}[htp]
    \begin{tabularx}{\textwidth}{llX}
        \toprule
        \textbf{Name}  & \textbf{Role}         & \textbf{Email Address}                 \\
        \midrule
        Imre Bakker    & Company Supervisor    & imre.bakker@stellarspaceindustries.com \\
        Philip Weersma & University Supervisor & philip.weersma@inholland.nl            \\
        Emil Boot      & Project Intern        & 661522@student.inholland.nl            \\
        \bottomrule
    \end{tabularx}
    \caption{Communication details}
    \label{table:comms}
\end{table}

\newpage
